Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/framework.tex

% TODO: For now, differential equation is the default, SDE is a footnote.
Let ${\cal S} = \mathbb{R}^d$ be a set of states, and ${\cal A}$ be a set of
actions. Consider the continuous-time \emph{Markov Decision Process} (MDP) defined by the differential equation %\TODO{Explain the intuition of Brownian in SDE}:
        \begin{equation}
	\label{eq:diffusion}
	ds_t/dt = F(s_t, a_t) % + \Sigma(s, a)\dbt.
              \end{equation}
where $F\colon {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
the dynamics of the environment. The agent interacts with the environment through a deterministic policy function
$\pi \colon {\cal S} \rightarrow {\cal A}$, so that $a_t=\pi(s_t)$;
actions can be discrete or continuous. 
For simplicity we assume here that both the dynamics and exploitation policy are
deterministic; \footnote{
      We believe the results presented here hold more
      generally, assuming states
      follow a \emph{stochastic} differential equation \begin{equation}
	      ds = F(s, a)dt  + \Sigma(s, a)\dbt
	      \label{eq:sde}
      \end{equation} with
      $B_t$ a multidimensional Brownian motion and $\Sigma$ a covariance matrix. A
      formal treatment of SDEs is beyond the scope of this paper.}
 the exploration policy will be random, but care must be
taken to define proper random policies 
in continuous time, especially with discrete actions (Sec.~\ref{subsec:explo}).

@@

\paragraph{Value function.}
The return \eqref{eq:continuous-return} leads to the
following continuous-time value function
\begin{align}
  V^\pi(s) &= \E_{\tau\sim\pi}\left[R(\tau) \mid s_0 = s\right]\\
  &= \E_{\tau\sim\pi}\left[\int\limits_{0}^\infty \gamma^{t}\, r(s_t,
  a_t) \,dt \mid s_0 = s\right].
\end{align}
Meanwhile, the value function (in the ordinary sense) of the discrete MDP ${\cal
M}_\deltat$ is
\begin{align}
  V^\pi_\deltat(s) &= \E_{\tau\sim\pi}\left[R_\deltat(\tau) \mid s_0 = s\right]\\
  &= \E_{\tau\sim\pi}\left[\sum\limits_{k=0}^\infty
  \gamma^{k\deltat}\,r(s_{k\deltat}, a_{k\deltat})\,\deltat \mid s_0 = s\right]
\end{align}
% which fits the usual definition of the discrete $V$-function for $\gamma_\deltat$ and
% $r_\deltat$ defined in \eqref{eq:def-gamma}.
which obeys the Bellman equation
\footnote{
If the continuous MDP follows the dynamics \eqref{eq:diffusion}, the limit of
the Bellman equation \eqref{eq:bellman} for $V^\pi_\deltat$ when $\deltat \rightarrow 0$ is
the \emph{Hamilton--Jacobi--Bellman} equation on $V^\pi$ \cite{cont_rl},
namely,
%\begin{equation}
  %\label{eq:hamilton-jacobi-bellman}
  $r + \nabla_s V^\pi \cdot F = - \log(\gamma) V^\pi$.
%\end{equation}
}
\begin{equation}
  \label{eq:bellman}
  V^\pi_\deltat(s) = \reward(s, \pi(s))\,\deltat + \gamma^{\deltat}\, \E_{s_{\deltat}^{k+1} | s_{\deltat}^{k} = s} V^\pi_\deltat(s_{\deltat}^{k+1})
\end{equation}

>>>>

% TODO: For now, differential equation is the default, SDE is a footnote.
Let ${\cal S} = \mathbb{R}^d$ be a set of states, and ${\cal A}$ be a set of
actions. Consider the continuous-time \emph{Markov Decision Process} (MDP) defined by the differential equation %\TODO{Explain the intuition of Brownian in SDE}:
        \begin{equation}
	\label{eq:diffusion}
	ds_t/dt = F(s_t, a_t) % + \Sigma(s, a)\dbt.
              \end{equation}
where $F\colon {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes
the dynamics of the environment. The agent interacts with the environment through a deterministic policy function
$\pi \colon {\cal S} \rightarrow {\cal A}$, so that $a_t=\pi(s_t)$.
Actions can be discrete or continuous. 
For simplicity we assume here that both the dynamics and exploitation policy are
deterministic; \footnote{
      We believe the results presented here hold more
      generally, assuming states
      follow a \emph{stochastic} differential equation \begin{equation}
	      ds = F(s, a)dt  + \Sigma(s, a)\dbt
	      \label{eq:sde}
      \end{equation} with
      $B_t$ a multidimensional Brownian motion and $\Sigma$ a covariance matrix. A
      formal treatment of SDEs is beyond the scope of this paper.}
 the exploration policy will be random, but care must be
taken to define proper random policies 
in continuous time, especially with discrete actions (Sec.~\ref{subsec:explo}).

@@

\paragraph{Value function.}
The return \eqref{eq:continuous-return} leads to the
following continuous-time value function
\begin{align}
  V^\pi(s) &= \E_{\tau\sim\pi}\left[R(\tau) \mid s_0 = s\right]\\
  &= \E_{\tau\sim\pi}\left[\int\limits_{0}^\infty \gamma^{t}\, r(s_t,
  a_t) \,dt \mid s_0 = s\right].
\end{align}
Meanwhile, the value function (in the ordinary sense) of the discrete MDP ${\cal
M}_\deltat$ is
\begin{align}
  V^\pi_\deltat(s) &= \E_{\tau\sim\pi}\left[R_\deltat(\tau) \mid s_0 = s\right]\\
  &= \E_{\tau\sim\pi}\left[\sum\limits_{k=0}^\infty
  \gamma^{k\deltat}\,r(s_{k\deltat}, a_{k\deltat})\,\deltat \mid s_0 = s\right]
\end{align}
% which fits the usual definition of the discrete $V$-function for $\gamma_\deltat$ and
% $r_\deltat$ defined in \eqref{eq:def-gamma}.
which obeys the Bellman equation
\footnote{
If the continuous MDP follows the dynamics \eqref{eq:diffusion}, the limit of
the Bellman equation \eqref{eq:bellman} for $V^\pi_\deltat$ when $\deltat \rightarrow 0$ is
the \emph{Hamilton--Jacobi--Bellman} equation on $V^\pi$ \cite{cont_rl},
namely,
%\begin{equation}
  %\label{eq:hamilton-jacobi-bellman}
  $r + \nabla_s V^\pi \cdot F = - \log(\gamma) V^\pi$.
%\end{equation}
}
\begin{equation}
  \label{eq:bellman}
  V^\pi_\deltat(s) = \reward(s, \pi(s))\,\deltat + \gamma^{\deltat}\,
  \E_{s_{(k+1)\deltat} | s_{k\deltat} = s} V^\pi_\deltat(s_{(k+1)\deltat})
\end{equation}
